Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
minor changes to abstract

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with object-based segmentation at larger timescales. Applying the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of the features designed using the wavelet scattering transform, consistently outperforming baseline mel-frequency cepstral coefficients (MFCCs).

In addition, representing the scene at larger time scale as a set of representative features from coherent segments is an effective approach for acoustic scene similarity retrieval as it allows the retrieval system to focus on discriminative features.
\end{abstract}

>>>>

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with object-based segmentation at larger timescales. Applying the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of the features designed using the wavelet scattering transform, consistently outperforming a baseline of mel-frequency cepstral coefficients (MFCCs).

In addition, representing the scene at larger time scale as a set of representative features from coherent segments is an effective approach for acoustic scene similarity retrieval, because it allows the retrieval system to focus on discriminative features.
\end{abstract}
